CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-18 paper.Rmd
Add Acknowledgement for PEB.

MKH acknowledges the support of Calvin University for 
a sabbatical during which he developed the PSUT framework
and course releases during which he wrote many of the `R` packages
described in this paper.
ZM's and PEB's time was funded by 
the UK Research Council under EPSRC Fellowship award EP/R024254/1.
EA's time was funded by 
the University of Leeds (School of Earth and Environment).

>>>>

M.K.H. acknowledges the support of Calvin University for 
a sabbatical during which he developed the PSUT framework
and course releases during which he wrote many of the `R` packages
described in this paper.
Z.M.'s time was funded by 
the UK Research Council under EPSRC Fellowship award EP/R024254/1.
E.A.'s time was funded by 
the University of Leeds (School of Earth and Environment).
M.K.H., Z.M., and E.A. are grateful for support and encouragement
from Paul E. Brockway (University of Leeds).
It is Paul's EPSRC fellowship that provided the need for the software
described in this paper.
